Copy number variants in rheumatoid arthritis data from inferCNV

### 2024-02-06 infercnv/reports/infercnv.Rmd
fix infercnv metadata propagation, change to standard mappings and annotations, add help nf functions

knitr::opts_knit$set(root.dir = '../')
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE,
  cache.path = 'reports/infercnv_cache/')

@@

```{r, results = 'asis'}
pngs <-
  list.files('out/Zhang2023/', pattern = '^BRI') %>%
  purrr::set_names() %>%
  purrr::map(function(sample_id) {
    lis <-
      list.files(paste0('out/Zhang2023/', sample_id), pattern = '.png', 
                 recursive = T, full.names = T) %>%
      {setNames(., gsub('infercnv.', '', tools::file_path_sans_ext(basename(.))))}

    # reorder
    c(lis['infercnv'], lis[names(lis) != 'infercnv'])
  })

@@

for (sample_id in names(pngs)) {

  chunks <- c(chunks, paste0('\n### ', sample_id))

  for (i in names(pngs[[sample_id]])) {

@@

    knit_plot <- c(
      '',
      '```{r, warning = F, message = F, echo = F}',
      paste0('knitr::include_graphics("../', pngs[[sample_id]][[i]], '")'),
      '```',
      ''
    )
    knitted_plot <- knitr::knit_child(text = knit_plot, envir = environment(), quiet = T)
    dev_off_if()

>>>>

# chunk options
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE)

@@

```{r, results = 'asis'}
pngs <-
  list.files(pattern = '^BRI', include.dirs = T) %>%
  purrr::set_names() %>%
  purrr::map(function(id) {
    lis <-
      list.files(id, pattern = '.png', recursive = T, full.names = T) %>%
      {setNames(., gsub('infercnv.', '', tools::file_path_sans_ext(basename(.))))}

    # reorder (final plot first)
    c(lis['infercnv'], lis[names(lis) != 'infercnv'])
  })

@@

for (id in names(pngs)) {

  chunks <- c(chunks, paste0('\n### ', id))

  for (i in names(pngs[[id]])) {

@@

    knit_plot <- c(
      '',
      '```{r, warning = F, message = F, echo = F}',
      paste0('knitr::include_graphics("../', pngs[[id]][[i]], '")'),
      '```',
      ''
    )
    knitted_plot <- knitr::knit_child(text = knit_plot, envir = environment(), quiet = T)
    dev_off_if()
